### 2022-01-21 input/abstract.tex
last sentence abstract

  %% \NAME is a crazy contribution
  \color{red}\NAME can constitute a new building block for
  geo-distribuetd service. Among the concrete use-cases we envision is
  the sharing of web objects regularly used in social networks (including viral pictures/video but also css,
  javascript objects): instead of contacting CDN nodes, it
  would be possible to retrieve objects closer and so mitigate the
  traffic overall.

>>>>

  %% \NAME is a crazy contribution
  \color{red} \NAME can constitute a novel building block for
  geo-distributed services, \eg sharing the locations of downloaded
  web objects to allow nodes benefit from neighborhood downloads,
  resource discovery in the vicinity of a region, etc.

%  javascript objects)
%  we envision is
%  the sharing of web objects regularly used in social networks (including viral picture/video but also css,
%  javascript objects): instead of contacting CDN nodes, it
%  would be possible to retrieve objects closer and so mitigate the
%  traffic overall.
